Blum axioms and nondeterministic computation of functions

### 2016-04-11 paper.tex
paper.tex: Argue why we choose strings instead of numbers for the definitions.

The concept of \emph{acceptable Gödel numbering}
(\cite[p.~41]{Rogers1987},~\cite[p.~324]{Blum1967})
encompasses the existence of universal machines and a little more.
We will use it as our reasonableness criteria to our definitions.

\begin{definition}
    Let $\mathcal P$ be the set of all partial recursive functions.
    An \emph{acceptable Gödel numbering}
    is a function $\phi : \{0, 1\}^* \to \mathcal P$,
    that associates each string (or program) $w \in \{0, 1\}^*$
    to a function $\phi_w \in \mathcal P$,
    that satisfies
    \begin{enumerate}
        \item $\phi$ is surjective;
            that is, every partial recursive function $f \in \mathcal P$
            has a program $w \in \{0, 1\}^*$ such that $\phi_w = f$;
            \label{surjectiveness}
        \item There is a partial recursive function
            $U:\{0, 1\}^* \times \{0, 1\}^* \to \{0, 1\}^*$ such that,
            for every $w$ and $x$,
            $U(w, x)$ is defined if and only if $\phi_w(x)$ is defined,
            and, in this case,
            \begin{equation*}
                U(w, x) = \phi_w(x);
            \end{equation*}
            \label{universal-tm}
        \item There is a total recursive function
            $\sigma:\{0, 1\}^* \times \{0, 1\}^* \to \{0, 1\}^*$ such that,
            for every $y$,
            $\phi_w(x, y)$ is defined if and only if $\phi_{\sigma(w, x)}(y)$ is defined,
            and, in this case,
            \begin{equation*}
                \phi_w(x, y) = \phi_{\sigma(w, x)}(y).
            \end{equation*}
            \label{smn-theorem}
    \end{enumerate}
\end{definition}

>>>>

The concept of \emph{acceptable Gödel numbering}
(\cite[p.~41]{Rogers1987},~\cite[p.~324]{Blum1967})
encompasses the existence of universal machines and a little more.
We will use it as our reasonableness criteria to our definitions.%

\begin{definition}
    Let $\mathcal P$ be the set of all partial recursive functions.
    An \emph{acceptable Gödel numbering}
    is a function $\phi : \{0, 1\}^* \to \mathcal P$,
    that associates each string (or program)\footnotemark $w \in \{0, 1\}^*$
    \footnotetext{
        In texts like Rogers'~\cite{Rogers1987},
        the partial recursive functions have the naturals as domain and codomain
        (that is, they are of the form $f: \mathbb N \to \mathbb N$),
        and Gödel numberings associates natural numbers with recursive functions.
        In this paper we will work with binary strings instead of numbers,
        which will simplify the definition of complexity classes
        and allows us to think the string $w$ as a \emph{program} for $\phi_w$
        (see example~\ref{c}).
    }
    to a function $\phi_w \in \mathcal P$,
    that satisfies
    \begin{enumerate}
        \item $\phi$ is surjective;
            that is, every partial recursive function $f \in \mathcal P$
            has a program $w \in \{0, 1\}^*$ such that $\phi_w = f$;
            \label{surjectiveness}
        \item There is a partial recursive function
            $U:\{0, 1\}^* \times \{0, 1\}^* \to \{0, 1\}^*$ such that,
            for every $w$ and $x$,
            $U(w, x)$ is defined if and only if $\phi_w(x)$ is defined,
            and, in this case,
            \begin{equation*}
                U(w, x) = \phi_w(x);
            \end{equation*}
            \label{universal-tm}
        \item There is a total recursive function
            $\sigma:\{0, 1\}^* \times \{0, 1\}^* \to \{0, 1\}^*$ such that,
            for every $y$,
            $\phi_w(x, y)$ is defined if and only if $\phi_{\sigma(w, x)}(y)$ is defined,
            and, in this case,
            \begin{equation*}
                \phi_w(x, y) = \phi_{\sigma(w, x)}(y).
            \end{equation*}
            \label{smn-theorem}
    \end{enumerate}
\end{definition}
